---
title: "July 29 2020 Group Work"
author: "Fred LaPolla"
date: "7/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Pulling in data

```{r, echo = TRUE}
library(RCurl)
url <- getURL("https://raw.githubusercontent.com/fredwillie/R_PhDProg_NYU_2020/master/Crusio1.csv")
crusio1 <- read.csv(text = url)
  
```


## Group Work

Try making a chart with both points and a line for center time vs center distance.

```{r}

```

## Group work

Make a histogram of center distance travelled, experiment with updating the binwidth. Make a boxplot of body weight by attack combined.

```{r}

```

## Group Work

Make a bar chart comparing the mean brainweight of attacking mice with error bars. 

```{r}

```


## Group Work

Explore the color brewer scales. Try using "display.brewer.all(colorblindFriendly = T)" to see the color blind friendly palettes. Add a color blind friendly palette to a chart of activity time vs. center distance, coloring by if they attacked or not (attack_combine)

```{r}

```

## Group Work

Make a chart of activity time vs. center distance and adjust the x access to have labeled breaks in increments of 2500 and the Y access in increments of 2000. 

```{r}

```

## Group Work

Copy your last chart and try out some of the themes available in Ggplot to update the background. What contexts would you want a lighter vs a darker background?

```{r}

```